---
title: "Symbolic Material Culture within an Ancient Catastrophic Temple Complex"
author: Dr. Henry Walton Jones Jr.
date: 1984-01-01
format: html
engine: knitr
execute: 
  warning: false
  echo: false
crossref: 
  tbl-prefix: "Tabelle"
  fig-prefix: "Abbildung"
---

```{r}
#| include: false 
library(tidyverse)
library(here)

mortuary_data <- read_csv(here("data/mortuary_clean.csv"))
```

# Title
## Section
### Subsection
#### etc.

## Introduction

This is a **totally made-up** study on a *completely* fictional archaeological
site.  
But the data are ***very*** real.

Create a new paragraph.

## Materials

Here is a list of excavation materials:

- Whip
  + for carefully excavating ancient material
- Hat
  + protection from sun
- Gun
  + keep away the cats
  
Order of priority:

1. Something
  i) Gun
      a. one more thing...
2. Stick
3. Whip
4. Hat

## Methods

I just learned R, and couldn't wait to use it. I'm using R version
`r version$version.string`.

## Results

```{r}
#| echo: false
#| label: tbl-summary-stats
#| tbl-cap: "This is a table."
mortuary_data |>
  group_by(Phase) |>
  summarise(
    mean = mean(Length, na.rm = T),
    sd = sd(Length, na.rm = T)
  ) |>
  arrange(desc(mean)) |>
  knitr::kable()
```


I did some things. I put them in @tbl-summary-stats.


Here is a figure.

```{r}
#| label: fig-boxplot
#| fig-cap: "This is a figure."
mortuary_data |>
  filter(Phase != "disturbed") |>
  ggplot(aes(x = Phase, y = Length, fill = Phase)) +
    geom_violin() +
    geom_boxplot(
      width = 0.2
    ) +
    theme_minimal()
```

All burials are pretty much the same across occupation phases (@fig-boxplot).






